Sound and Automated Synthesis of Digital\\ Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-03-03 hscc2017/paper.tex
page breaks
SWATI paper

%------------------------------------
\subsection{Model Imprecision, Finite Word Length Representation and Quantization Effects}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

Other tools such as~\cite{economakos2016automated} are aimed at
robust stability problems, but they fail to take the FWL effects into
account.  In order to provide a correct-by-design digital controller,
\cite{alur2016compositional} requires a user-defined finite-state
abstraction to synthesize a digital controller based on high-level
specifications.  While this approach overcomes the challenges presented by
the FWL problem, it still requires error-prone user intervention. 
A~different solution that uses FWL as the starting point is an approach that
synthesizes word lengths for known control problems~\cite{jha2013swati};
however, this provides neither an optimal result nor a comprehensive
solution for the problem.

@@

We have presented a method for synthesizing stable controllers, implemented
in a tool called \tool.  Our approach is it is fully automated and
algorithmically and numerically sound.  \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  We transform the traditional CEGIS refinement loop into
a two-stage engine: here, the first stage performs fast, but potentially
unsound fixed-point operations, whereas the second stage restores soundness
by validating the operations performed by the first stage using interval
arithmetic.  Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  Future work will be the extension of this CEGIS-based
approach to further classes of systems, including those with state space. 
We will also consider performance requirements while synthesizing the
digital controller.

\newpage
\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

%------------------------------------
\newpage
\subsection{Model Imprecision, Finite Word Length Representation and Quantization Effects}
\label{verifying-closed-loop-control-systems}
%------------------------------------

@@

Other tools such as~\cite{economakos2016automated} are aimed at
robust stability problems, but they fail to take the FWL effects into
account.  In order to provide a correct-by-design digital controller,
\cite{alur2016compositional} requires a user-defined finite-state
abstraction to synthesize a digital controller based on high-level
specifications.  While this approach overcomes the challenges presented by
the FWL problem, it still requires error-prone user intervention. 
A~different solution that uses FWL as the starting point is an approach that
synthesizes word lengths for known control problems~\cite{jha-nsv13};
however, this provides neither an optimal result nor a comprehensive
solution for the problem.

@@

We have presented a method for synthesizing stable controllers, implemented
in a tool called \tool.  Our approach is it is fully automated and
algorithmically and numerically sound.  \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  We transform the traditional CEGIS refinement loop into
a two-stage engine: here, the first stage performs fast, but potentially
unsound fixed-point operations, whereas the second stage restores soundness
by validating the operations performed by the first stage using interval
arithmetic.  Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  Future work will be the extension of this CEGIS-based
approach to further classes of systems, including those with state space.

%Finally, we will consider performance requirements.

%\newpage
\bibliographystyle{abbrv}
\bibliography{paper}
